A coupled particle level set and Moment-of-fluid method for simulating multiphase flows with phase change \thanks{this material is based upon work supported by National Aeronautics and Space Administration under grant number 80NSSC20K0352}

### 2024-06-12 main.tex
updating tables
modify the freezing parts a little

\begin{figure}[htbp]
\centering
\includegraphics[width=0.4\textwidth]{checkerboardMOF.eps}
\includegraphics[width=0.4\textwidth]{checkerboardPLSMOF.eps}
%%\includegraphics[width=0.4\textwidth]{checkerboardCMOF.eps}
%%REMMERSWAAL and Veldman's parabolic reconstruction WILL NOT SEE
%%the checkerboard pattern (even though they take both F and x into
%%account).
\caption{LEFT:
 Standard curvature discretization methods 
 \cite{sussman2003second,cummins2005estimating,REMMERSWAAL2022111473}
 will predict zero curvature for this saw-tooth
 interface since the volume fractions {\em and} 
 centroids vary only
 in the $y$ direction.  Repeated Moment-of-Fluid (MOF)
 (i) reconstruction followed by (ii) the replacement of the reference
 centroid with the MOF actual centroid will not alter the initial interface
 (ignoring round-off error).  RIGHT: the gaps in the initial saw-tooth 
 interface are immediately removed with PLSMOF reconstruction since the
 level set function is derived as the exact signed distance function to the
 initial MOF reconstructed interface, and the particles are initialized from
 the level set function.  Ensuing slopes
 are derived from a combination of the particles and the signed
 distance function (if particles available).
 \label{checkerboard} }
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.7\textwidth]{ice_levelset.eps}
        \caption{Level set functions for the simulation of 
	the freezing of a water drop on top of a cold substrate.
	The temperature in the substrate, $T_{w}$, is prescribed.
        The ice, water, and air deforming materials tessellate
        the computational domain.
        $\phi_{\mbox{substrate}}>0$ in the cold substrate,
        $\phi_{\mbox{ice}}>0$ in the ice and 
        $\phi_{\mbox{water}}>0$ in the water.  The
        ice/air interface is extended into the substrate.
        Note: the ice is a deforming material solely due to 
        phase change at the ice/water interface.
        Following the freezing model presented in \cite{lyu2021hybrid}, the
        ice and water materials are considered as the same
        material when calculating the surface tension force 
        at the water/ice/air triple point.
        In other words, the interfacial
        curvature both at and away from triple points is computed using
        the Volume of fluid height function technique
        \cite{sussman2003second}.
    }
  \label{ice_levelset}
\end{figure}

@@

\begin{table}[h!]
	\caption{Time to freeze a water droplet with 
	initial volume $4.95e-5\mbox{cm}^{3}$ as a 
	function of the wall temperature (degrees Celsius)
	and Latent heat.  Results are
	compared with experiments from \cite{hu2010icing}.  
	Much closer agreement is made with experiments when
	the latent heat is prescribed as $65.0e+9$ as opposed
	to when he latent heat is the physical value
	$3.34e+9$.
}
% -6, fine, 0.579
% -6, med, 0.590
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Wall temperature & Latent heat & time (computed) & time (exp) 
	 \\ \hline
$-2.0$ & $3.34e+9$ & $2.0$ & $32.5$ \\ \hline
$-3.0$ & $3.34e+9$ & $1.2$ & $21.0$ \\ \hline
$-4.0$ & $3.34e+9$ & $0.9$ & $16.0$ \\ \hline
$-5.0$ & $3.34e+9$ & $0.7$ & $13.5$ \\ \hline
$-2.0$ & $65.0e+9$ & $35.7$ & $32.5$ \\ \hline
$-3.0$ & $65.0e+9$ & $22.6$ & $21.0$ \\ \hline
$-4.0$ & $65.0e+9$ & $16.7$ & $16.0$ \\ \hline
$-5.0$ & $64.0e+9$ & $13.0$ & $13.5$ \\ \hline
\end{tabular}
\label{freezing_time}
\end{table}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[width=0.4\textwidth]{checkerboardMOF.eps}
%%\includegraphics[width=0.4\textwidth]{checkerboardPLSMOF.eps}
%%\includegraphics[width=0.4\textwidth]{checkerboardCMOF.eps}
%%REMMERSWAAL and Veldman's parabolic reconstruction WILL NOT SEE
%%the checkerboard pattern (even though they take both F and x into
%%account).
\caption{LEFT:
 Standard curvature discretization methods 
 \cite{sussman2003second,cummins2005estimating,REMMERSWAAL2022111473}
 will predict zero curvature for this saw-tooth
 interface since the volume fractions {\em and} 
 centroids vary only
 in the $y$ direction.  Repeated Moment-of-Fluid (MOF)
 (i) reconstruction followed by (ii) the replacement of the reference
 centroid with the MOF actual centroid will not alter the initial interface
 (ignoring round-off error).  RIGHT: the gaps in the initial saw-tooth 
 interface are immediately removed with PLSMOF reconstruction since the
 level set function is derived as the exact signed distance function to the
 initial MOF reconstructed interface, and the particles are initialized from
 the level set function.  Ensuing slopes
 are derived from a combination of the particles and the signed
 distance function (if particles available).
 \label{checkerboard} }
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.7\textwidth]{ice_levelset.eps}
        \caption{Level set functions for the simulation of 
	the freezing of a water drop on top of a cold substrate.
	The temperature in the substrate, $T_{w}$, is prescribed.
        The ice, water, and air deforming materials tessellate
        the computational domain.
        $\phi_{\mbox{substrate}}>0$ in the cold substrate,
        $\phi_{\mbox{ice}}>0$ in the ice and 
        $\phi_{\mbox{water}}>0$ in the water.  The
        ice/air interface is extended into the substrate.
        Note: the ice is a deforming material solely due to 
        phase change at the ice/water interface.
	Two freezing models are implemented: (A) for comparison with
        \cite{hu2010icing}, we follow the 
        freezing model presented in \cite{lyu2021hybrid}. The
        ice and water materials are considered as the same
        material when calculating the surface tension force 
        at the water/ice/air triple point.
        In other words, the interfacial
        curvature both at and away from triple points is computed using
        the Volume of fluid height function technique
	\cite{sussman2003second}.  (B) for comparison with Vu et al
	\cite{vu2013front}, we treat the ice material as a rigid solid in 
	prescribing the contact angle boundary conditions.
    }
  \label{ice_levelset}
\end{figure}

@@

\begin{table}[h!]
	\caption{Time to freeze a water droplet with 
	initial volume $4.95e-5\mbox{cm}^{3}$ as a 
	function of the wall temperature (degrees Celsius)
	and Latent heat.  Simulations sharply ``capture'' 
        the triple point dynamics at the ice, water, and air 
        interface using the hybrid PLS-MOF method.
        Results are
	compared with experiments from \cite{hu2010icing}.  
	Much closer agreement is made with experiments when
	the latent heat is prescribed as $65.0e+9$ as opposed
	to when he latent heat is the physical value
	$3.34e+9$.
}
%MAT=2 dir= 1 GLOBAL MAX INT=
% -6, coarse, 0.543
% -6, fine, 0.504
% -6, med, 0.517
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Wall temperature & Latent heat & time (computed) & time (exp) 
	 \\ \hline
$-2.0$ & $3.34e+9$ & $1.7$ & $32.5$ \\ \hline
$-3.0$ & $3.34e+9$ & $1.1$ & $21.0$ \\ \hline
$-4.0$ & $3.34e+9$ & $0.8$ & $16.0$ \\ \hline
$-5.0$ & $3.34e+9$ & $0.6$ & $13.5$ \\ \hline
$-2.0$ & $65.0e+9$ & $31.8$ & $32.5$ \\ \hline
$-3.0$ & $65.0e+9$ & $20.3$ & $21.0$ \\ \hline
$-4.0$ & $65.0e+9$ & $14.9$ & $16.0$ \\ \hline
$-5.0$ & $64.0e+9$ & $11.7$ & $13.5$ \\ \hline
\end{tabular}
\label{freezing_time}
\end{table}
